---
title: "tabde"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{tabde}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

```{r setup}
library(tabde)
```

# SQL constraints and periods

tabde allows for table_design `.csvy` files that contain metadata on SQL 
constraints and periods in a yaml header. 

The simplest and most flexible way is to specify the constraints and periods as 
raw SQL. Please note that the `:` at the end of each row is required to make the 
header valid yaml.
```{}
#---
#CONSTRAINT MYKEY PRIMARY KEY (ID, business_time without overlaps):
#CONSTRAINT MYUNIQUE UNIQUE (ID2):
#PERIOD business_time (BEGIN, END):
#---
col_name;col_type;sql_type;sql_opts;comment
```


The columns for each constraint/period can also be specified as yaml bullet
lists
```{}
#---
#CONSTRAINT MYKEY PRIMARY KEY:
#  - ID
#  - business_time without overlaps
#
#CONSTRAINT MYUNIQUE UNIQUE:
#  - ID
#
#PERIOD business_time:
#  - BEGIN
#  - END
#---
col_name;col_type;sql_type;sql_opts;comment
```

Alternatively, there is also a more formal way to supply the constraints
as pure yaml. Currently only constraints and periods are supported this way.
```{}
#---
#period:
#  business_time:
#    columns:
#      - BEGIN
#      - END
#
#constraint:
#  MYKEY:
#    type: "PRIMARY KEY"
#    columns:
#      - ID
#      - business_time without overlaps
#
#  MYUNIQUE:
#    type: "UNIQUE"
#    columns:
#      - ID2
#---
col_name;col_type;sql_type;sql_opts;comment
```


